%\documentclass{article}
\documentclass[10pt]{res}

\usepackage{helvet}
\usepackage{hyperref}
\usepackage{bibentry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\title{Javad Amirian}
%\subtitle{Resume}
\author{Javad Amirian}
\date{2016-05-30}

\newsectionwidth{0pt}

\begin{document}

\name{Javad Amirian\\ \\}
\vspace{28pt}

%\section{\centerline{Contact Information}}

%\address{{\bf Permanent Address} \\ \\  \\  % Your address 1
\address{{\bf Address} \\ 263 Avenue Général Leclerc \\
	Campus de Beaulieu, Inria \\ 35042 Rennes, France } % Your address 1


\address{{\bf Contact} \\ 
Mobile: +33 6 32 38 50 50\\
%mail: amiryanj@ce.sharif.edu \\
mail: javad.amirian@inria.fr \\
http://\url{http://people.rennes.inria.fr/Javad.Amirian/} } % Your address 2


\begin{resume}


\section{\centerline{Research Interests}}
\vspace{8pt} % Gap between title and text

\begin{itemize} \itemsep -1pt
\item Computer Vision
\item Deep Learning and Generative Models
\item Crowd Simulation and Motion Planning
\end{itemize}

\section{\centerline{Education}}
\vspace{8pt} % Gap between title and text
{\sl PhD Candidate}\\
Inria, Rennes, France \hfill 2018-2021\\
Title: Short-term Pedestrian Prediction for Robot Navigation in Crowded Space


{\sl Master of Science} in Computer Engineering (Artificial Intelligence) \\ 
Sharif University of Technology, Tehran, Iran \hfill 2012 - 2014\\ 
%THESIS - Job Evaluation: Dynamic Motion Planning and Obstacle Avoidance Simulation for Autonomous Robot-Car in Webots \\
GPA: 16.66/20\\
Ranked 11th in nationwide M.Sc. university entrance exam for Artificial Intelligence, Iran \hfill 2012
 
{\sl Bachelor of Science} in Electrical Engineering (Electronics) \\ 
Shahid Behesti University (National University of Iran), Tehran, Iran \hfill 2007 - 2012\\
GPA: 15.44/20\\
Top 0.6\% nationwide entrance exam of Iranian Universities, among more than 300,000 participants. \hfill 2007

{\sl Diploma} in Mathematics and Physics \\
Tiz-Hooshan School (National Org for Development of Exceptional Talents), Kermanshah, Iran \hfill 2000 - 2007\\
GPA: 18.00/20


%-----------------------------------------------------------
\vspace{-8pt} % Negative space between title and text
 

%\section{\centerline{Graduate Courses}}
%\vspace{8pt} % Gap between title and text
%Machine Learning, Statistical Pattern Recognition, Computational Intelligence, Image Processing, Planning in Artificial Intelligence, Speech Processing, Stochastic Processes.


% Main Projects
\section{\centerline{Professional Experience}}
\vspace{-6pt} % Negative space between title and text

\paragraph{Research and Develop @ {CrowdBot}}(European H2020 Research Project) \hfill 2018 - 2021\\
CrowdBot is a H2020 European project, aiming to develop platforms and algorithms to ensure safe navigation of social robots.
My main task is to develop tools for "Trajectory Prediction" of the agents around the robot, in order to improve the robot navigation in crowded environments. For that, I'm working with Crowd Simulation algorithms and developing Deep Generative models.

\paragraph{Computer Vision Engineer @ \href{http://pixballsports.com}{PixBall}}  \hfill May 2015 - present\\
PixBall is an AI startup providing smart solutions for sports analysis. My job is developing image processing and vision algorithms and providing high-level API for UI programmers. I contributed to PixArt, a software video processing solution for inserting graphical overlays and virtual advertisements into sports content.  One of the main challenges in such a system is to estimate camera calibration based on corresponding points in the soccer pitch. The vision engine is composed of several processing modules including the estimation of camera position, finding initial camera pose, using exhaustive search algorithms, shot boundary detection, tracking of camera calibration parameters, to which I contributed.

\paragraph{Computer Vision Expert @ \href{http://www.spadsystem.com/}{Spad System Co.} } \hfill April 2016 - present\\
Spadsystem is a startup founded in 2013, specialized in traffic management solutions. In 2016, I joined the team to start a project for automatic recognition of Iranian license plates \href{http://didbaan.com}{(Didbaan)}. I developed a ALPR engined based on an open-source software (OpenALPR). This software has been in use to manage the entrance and exit of cars from parking in multiple sites.
%I designed a tool for detecting moving objects using motion segmentation technique and also optimized an existing LBP descriptor to find the plates regions in the image. Furthermore I implemented a Persian OCR module using standard C++ libraries to extract the content of the plates.

% describe small size project
\paragraph{Co-Founder and Team Leader @ {Cyrus}}(Team of Small-Size Soccer Robots) \hfill 2010 - 2015\\
%A team of 6 small mobile robots play soccer on a green carpeted field that is 9 m long by 6 m wide. Small Size robot soccer focuses on the problem of intelligent multi-agent cooperation and control in a highly dynamic environment with a hybrid centralized/distributed system. 
I co-founded \textbf{Cyrus} under the supervision of Dr. Eslam Nazemi, during my undergrad study. I collaborated with more than 20 undergrad and graduate students that joined the team to develop hardware and software of the robots and prepare them for Robocup competitions. My main role was in the technical management of the project. Moreover,  I contributed to designing the electronic boards, programming the robot firmware, and latterly developing codes for motion planning and playing of the robots. As research results of the project, we presented a new approach to improve the robot movements and compensating inaccuracies in robot building using a Fuzzy approach. We also proposed a new motion-planning algorithm for the robots, that is able to adapt the navigation parameters by optimizing multiple objectives, simultaneously.




%\section{\centerline{Work Experience}}
\section{\centerline{Teaching Experience}}
\vspace{15pt}
\begin{itemize} \itemsep -1pt

\item {\sl Teaching Assistant} of Numerical Optimization course \hfill Spring 2017\\
Dr. S. Hamid Amiri (Shahid Rajaee University) 

\item {\sl Teaching Assistant} of Machine Vision course (CE-40687) \hfill Spring 2014\\
Dr. Mansour Jamzad (Sharif University of Technology)

\item {\sl Teaching Assistant} of Digital Design course \hfill Spring 2010, Spring 2011\\
Dr. Somayeh Timarchi (Shahid Beheshti University)

\item {\sl Lecturer} of Introduction to AVR Microcontrollers \hfill 2009-2011\\
At Scientific Association of Electrical Engineering (Shahid Behshti University) 

\end{itemize}



\section{\centerline{Selected Publications}}
\vspace{15pt} % Gap between title and text
%{\bf Conference Papers}\\

\begin{itemize} \itemsep -1pt % Reduce space between items

\item {\bf Amirian, J.}, Zhang, B., Valente Castro, F., Baldelomar, J., Hayet, J. B., Pettré, J. (2020, Dec). {\bf ''OpenTraj: Assessing Prediction Complexity in Human Trajectories Datasets.''} In Proceedings of the 15th Asian Conference on Computer Vision.


\item {\bf Amirian, J.}, Van Toll, W., Hayet, J. B., Pettré, J. (2019, July). {\bf ''Data-Driven Crowd Simulation with Generative Adversarial Networks.''} In Proceedings of the 32nd International Conference on Computer Animation and Social Agents (pp. 7-10).

\item {\bf Amirian, J.}, Hayet, J. B., Pettré, J., {\bf ''Social ways: Learning multi-modal distributions of pedestrian trajectories with GANs,''} IEEE Conference on Computer Vision and Pattern Recognition Workshops, 2019.

\item (TDP) {\bf Amiryan, J.}, Raeessi, S., Payandeh, P., Nadimi, B., Nouri, N., Kamali, M. R., Nazemi, E., {\bf ''CYRUS 2016 Team Description Paper,''} 2016.

\item {\bf Amiryan, J.}, Jamzad, M., {\bf ''Adaptive motion planning with artificial potential fields using a prior path,''} Robotics and Mechatronics (ICROM), 2015 3rd RSI International Conference on, 2015.

\item (MSc Thesis) {\bf Amiryan, J.}, {\bf ''Dynamic Motion Planning and Obstacle Avoidance Simulation for Autonomous Robot-car in Webots,''} MSc Thesis, Department of Computer Engineering, Sharif University of Technology, August 2014.

\item Mazloum, J., Jalali, A., {\bf Amiryan, J.}, {\bf ''A novel bidirectional neural network for face recognition,''} Computer and Knowledge Engineering (ICCKE), 2012 2nd International eConference on. IEEE, 2012.

%\item (BSc Project Report) {\bf J. Amiryan,} J. Kamali, {\bf ''Automatic Traffic Control System With Police Robot,''} BSc. Thesis, Department of Electrical Engineering, Shahid Beheshti University, March 2012.
\end{itemize}

\section{\centerline{Skills}}
\vspace{15pt}
\begin{itemize} \itemsep -1pt

%\item {\bf OS:} Microsoft Windows; Linux (Ubuntu, Fedora, CentOS); Android.
%\item {\bf Office Tools:} \LaTeX; Libre Office; Microsoft Word, Excel, PowerPoint, Visio.
\item {\bf Programming Languages:} Python, C/C++, Matlab.
\item {\bf Deep Learning Frameworks:} Pytorch, Keras (TensorFlow)
\item {\bf Version Control:} Git.
\item {\bf AI and Robotics Tools:} OpenCV, ROS.
\item {\bf Software Design:} OOD; Concurrent and Multithread; Modular Programming.
%\item {\bf Database:} PostgreSQL, ODB (ORM).
\item {\bf Graphic Tools:} Adobe Photoshop, Adobe Premiere; 3ds Max.
%\item {\bf Embedded Design:} ARM Processors (AT91, LPC), Atmel AVR Family, C51 Family; Altium Designer, Proteus, Protel.

\end{itemize}



\section{\centerline{Activities}}
\begin{itemize}
%\item I love robots and robotic competitions, I have participated in many robotic events in fields of intelligent mouses and soccer robots.
\item Former member of technical committee (TC) of Small Size League at Robocup Iran Open. \href{http://2017.iranopen.ir/en-gb/leagues/robocupsoccer/smallsizerobotleague.aspx}{Link}.

\item Interested in football and fan of Perspolis club. Going to stadium and encouraging my favorite team is one of my most exciting entertainments.

\item Interested in playing soccer, hiking, body-building.

\end{itemize}


\section{\centerline{References}}

\begin{itemize}
\item   {\bf \href{http://people.rennes.inria.fr/Julien.Pettre} {Dr. Julien Pettre} }\\
Research Scientist at Rainbow, INRIA-Rennes, Brittany, France\\
Email: julien.pettre@inria.fr


\item   {\bf \href{http://aplicaciones.cimat.mx/Personal/jbhayet} {Dr. Jean-Bernard Hayet} }\\
Researcher at CIMAT, Department of Computer Science., Guanajuato, Mexico\\
Email: jbhayet@cimat.mx


\item   {\bf \href{http://ce.sharif.edu/~jamzad} {Dr. Mansour Jamzad} }\\
Department of Computer Engineering, Sharif University of Technology,Tehran, Iran\\
Email: jamzad@sharif.edu

\item   {\bf  Dr. Eslam Nazemi}\\
Department of Electrical and Computer Engineering, Shahid Beheshti University, Tehran , Iran\\
Email: nazemi@sbu.ac.ir

%\item   {\bf \href{http://facultymembers.sbu.ac.ir/eshghi/}{Dr. Mohamad Eshghi} }\\
%Department of Electrical and Computer Engineering, Shahid Beheshti University, Tehran , Iran\\
%Email: m-eshghi@sbu.ac.ir

\end{itemize}

\end{resume}


\end{document}
